Stable Neo-Hookean Flesh Simulation

### 2019-11-25 LaTeX-Master-Vorlage/chapter/paper.tex
existing energies getting better

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Energy} & \textbf{Author(s)} \\ \hline
    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ & Mooney 1940 \\ \hline
    $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 \\ \hline
    $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 \\ \hline
    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)$ & Wang and Yang 2016 \\ \hline
    \end{tabular}
    \caption{Summary of proposed energies taken from \cite{Smith:2018:SNF:3191713.3180491}}
\label{table:1}
\end{table}

@@

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l | l |}
    \hline
    \textbf{Energy} & \textbf{1D length term} & \textbf{3D volume term} \\ \hline
    $\Psi_{Neo}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ \\ \hline
    $\Psi_{\mathrm{A}}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
    $\Psi_{\mathrm{B}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
    $\Psi_{\mathrm{C}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+$ & $\frac{\lambda}{2}(J-1)$ \\ \hline
    \end{tabular}
    \caption{Energies split up into its 1D length and 3D volume term}
\label{table:1}
\end{table}

\textbf{1D Length Term:} This term penalizes length changes. Mooney proposed the energy (\cite{mooney1940theory})
\[
\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right)
\]
which was later known as "Neo-Hookean" energy.

If we expand the energy with the singular values of the deformation gradient \textbf{F} we get the following term:
\[
\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right) = \frac{\mu}{2}\left(\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2 - 3\right)
\]

The energy as it is formulated reaches its minimum at a zero volume change, meaning $I_{C}=0$ and $\Psi_{M}=-3$. Mooney added the hard constraint that $J=1$ so that the energy is minimized at the volume preserving configuration. Note that the energy is singularity free and well defined under inversion.

>>>>

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Energy} & \textbf{Author(s)} \\ \hline
    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ & e.g. Bonet and Wood 2008 \\ \hline
    $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 \\ \hline
    $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 \\ \hline
    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)$ & Wang and Yang 2016 \\ \hline
    \end{tabular}
    \caption{Summary of proposed energies taken from \cite{Smith:2018:SNF:3191713.3180491}}
\label{table:1}
\end{table}

@@

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l | l |}
    \hline
    \textbf{Energy} & \textbf{1D length term} & \textbf{3D volume term} \\ \hline
    $\Psi_{Neo}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ \\ \hline
    $\Psi_{\mathrm{A}}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
    $\Psi_{\mathrm{B}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
    $\Psi_{\mathrm{C}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $\frac{\lambda}{2}(J-1)$ \\ \hline
    \end{tabular}
    \caption{Energies split up into its 1D length and 3D volume term}
\label{table:1}
\end{table}

\textbf{1D Length Term:} This term penalizes length changes. Mooney (\cite{mooney1940theory}) originally proposed the 1D length term 
\[
\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right)
\]
that is used in $\Psi_{Neo}$ and $\Psi_{A}$. If we expand the energy with the singular values of the deformation gradient \textbf{F} we get the following term:
\[
\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right) = \frac{\mu}{2}\left(\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2 - 3\right)
\]
The energy as it is formulated reaches its minimum at a zero volume change, meaning $I_{C}=0$ and $\Psi_{M}=-3$. Mooney added the hard constraint that $J=1$ so that the energy is minimized at the volume preserving configuration. Note that the energy is singularity free and well defined under inversion.

The second term 
\[
\Psi_{R} = \frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)
\]
is used in $\Psi_{B}$ and $\Psi_{C}$ was introduced by Rivlin in 1948. Using the singular values of F we get the following term:
\[
\Psi_{R} = \frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right) = \frac{\mu}{2}\left(\frac{\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2}{(\sigma_{0}  \sigma_{1}  \sigma_{2})^\frac{2}{3}}
 - 3\right)
\]
Unfortunately this term is not singularity free. If either $\sigma_{0}$, $\sigma_{1}$ or $\sigma_{2}$ is equal to zero the result is not defined anymore.
